\section{Warmup}

\begin{table}[hb]
\center
\begin{tabular}{|l|l|l|}
\hline
\textbf{Word 1} & \textbf{Word 2} & \textbf{Cosine Similarity} \\ \hline
cat             & dog             & 0.7502321004867554         \\ \hline
cat             & Vienna          & 0.17059043049812317        \\ \hline
Vienna          & Austria         & 0.7768975496292114         \\ \hline
Austria         & dog             & 0.2197847068309784         \\ \hline
\end{tabular}
\end{table}

The calculated cosine similarities are sound.
A high similarity was calculated for \enquote{Vienna} and \enquote{Austria}, since the former is the capital of the latter.
On the same note, the cosine similarity of \enquote{cat} and \enquote{dog} is high, as both are common pets.
In contrast, \enquote{cat} and \enquote{Vienna} as well as \enquote{Austria} and \enquote{dog} have much lower cosine similarities.
This matches expectations, as the words of both pairs are semantically very different.

\begin{table}[hb]
\center
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{Word} & \textbf{Top-1} & \textbf{Top-2} & \textbf{Top-3} \\ \hline
Vienna        & Salzburg       & Austria        & Prague         \\ \hline
Austria       & Austria-       & Vienna         & German-Austria \\ \hline
cat           & cats           & housecat       & -cat           \\ \hline
\end{tabular}
\end{table}

The top three most similar words for \enquote{Vienna}, \enquote{Austria} and \enquote{cat} are reasonable results.

\paragraph{Vienna}
The connection to \enquote{Salzburg} and \enquote{Austria} are trivial. Both Salzburg and Vienna are large cities (and states) in Austria.
\enquote{Prague} being similar to Vienna is also reasonable, as it is the capital of the Czech Republic and located geographically close.

\paragraph{Austria}
\enquote{Austria-} and \enquote{German-Austria} being in the top three most similar words is understandable, as both contain the word \enquote{Austria} and are probably used in similar contexts.
Vienna is the capital of Austria, hence the relation is sound.

\paragraph{cat}
The explanation of the results is once again trivial.
All three words contain \enquote{cat} and are highly related from a semantic point of view.
